Poseidon Adventure

### 2020-06-01 NOBAcod.Rmd
NOBA cod data generation, all but WtAtAnnage

**Special note:** *Atlantis output files usually have the prefix "output" and `atlantisom` expects this. NOBA output files use a different naming convention. I've appended "output" to the beginning of each NOBA output filename for `atlantisom` to work. Need to update `atlantisom` functions for user-specified output filenames.*

@@

### Using the wrappers

@@

#### Fishery age composition (age classes)
```{r agecomp-1}

@@

Wrappers work for NOBA cod using standard age classes.

@@

### Wrapper test results for annual ages {#annageoutput}{.tabset}

@@

#### Survey weight at age (annual ages)
```{r plot-annwtage}

@@

UPDATE: there is a difference between the annage weight at age and that calculated using 'calc_age2length'. While the results from the standard nc output look reasonable for NOBA cod, the annage weight at age is half that for the standard (and half what real cod would be). More worrisome, the oldest age classes have smaller average weight at age than some younger ones. I cannot think of why this would be. Until we are sure the annage weight output is correct, we will instead interpolate the weight at age output of 'calc_age2length" for use as assessment input.

@@

New function `load_fisheries` needed to load the fishery specification file (a .csv), similar to `load_fgs`:

@@

Call `load_fisheries` within `load_nc_annage` to rename select_variable as used in ANNAGECATCH.nc:

@@

Test new `load_nc_annage`:

@@

Now all of the wrappers need to read from annage to produce composition data. `om_init()`  now takes annage flag from the config file. `om_species()` looks for annage bio and catch output in the truth file and includes it in the species file (adding NULL if it isn't there).

@@

Running om_init, om_species, om_index, om_comps in chunk above, plot the annage output [above](#annageoutput).

>>>>

**Special note:** *Atlantis output files formerly had the prefix "output" and `atlantisom` was coded to expect this. NOBA output files (and newer Atlantis models) do not universally use the "output" prefix naming convention. Annage branch `atlantisom` functions have been updated for user-specified output filenames.*

@@

### Using the wrappers (now updated for annual age)

@@

#### Fishery age composition (age classes)
```{r fishagecomp-1}

@@

Wrappers still work for NOBA cod using standard age classes.

@@

### Wrapper test results for annual ages {.tabset #annageoutput}

@@

#### Survey weight at age (annual ages) pending new function
```{r plot-annwtage}

@@

UPDATE: there is a difference between the annage weight at age and that calculated using 'calc_age2length()'. While the results from the standard nc output look reasonable for NOBA cod, the annage weight at age is half that for the standard (and half what real cod would be). More worrisome, the oldest age classes have smaller average weight at age than some younger ones. I cannot think of why this would be. Until we are sure the annage weight output is correct, we will instead interpolate the weight at age output of 'calc_age2length" for use as assessment input.

@@

New function `load_fisheries()` needed to load the fishery specification file (a .csv), similar to `load_fgs()`:

@@

Call `load_fisheries()` within `load_nc_annage()` to rename select_variable as used in ANNAGECATCH.nc:

@@

Test new `load_nc_annage()`:

@@

Now all of the wrappers need to read from annage to produce composition data. `om_init()`  now takes annage flag from the config file. `om_species()` looks for annage bio and catch output in the truth file and includes it in the species file (adding NULL if it isn't there). `om_comps()` looks for annage bio and catch in the species file and adds them to the comps list if there (adding NULL if they aren't there).

@@

Running `om_init()`, `om_species()`, `om_index()`, `om_comps()` in chunk above to make sure the original output is preserved, then plot the annage output [above](#annageoutput).

### 2020-06-01 docs/index.Rmd
NOBA cod data generation, all but WtAtAnnage

<a href="https://sgaichas.github.io/poseidon-dev/NOBAcod.html" target="_blank">Apply and extend wrappers to get full age structure, updated May 22, 2020</a>

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/NOBAcod.html" target="_blank">Apply and extend wrappers to get full age structure, updated June 1, 2020</a>
